Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
fix README md file

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) %>% 
  as_raw_html()
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) %>% 
  as_raw_html()
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) %>% 
  as_raw_html()
```

>>>>

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything()) 
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything())
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>%
  gt(id = "one", rowname_col = "row") %>% 
  fmt_markdown(columns = everything())
```
